%------------------------------------------------------------------------------
\chapter*{Acknowledgements}
\label{sec:ack}
%------------------------------------------------------------------------------

This thesis would not be possible without the support of many people. I would like to gratefully acknowledge all of them, in particular, those people that supervised my work, those that I have worked with, and those who have shared their knowledge with me. 

Firstly, I would like to express my sincere gratitude to Prof. Dr. Ian C. Brock for accepting me to work on the analysis presented in this thesis, for his support and guidance throughout the year. I am very grateful to Prof. Dr. Klaus Desch who agreed to be the second supervisor for this thesis. 

This analysis is a result of the collaboration by a group of people from all over the globe. I would like to acknowledge the support of everyone involved in particular Lidia Dell'Asta, Alberto Plebani, Muhammad Alhrood, and Thomas Stevenson. 

This work would not have been possible without the support of the Brock research group especially Tanja Holm, Oleh Kivernyk, Christain Kirfel, Chris Staude, and Nilima Akolkar. I could not even imagine the completion of this thesis without the guidance, support, and kindness of Tanja Holm and Lidia Dell'Asta. Besides, many thanks to the tHq collaborations for Eventloop framework, Rico and Christain for their neural network framework. 

Of course, I can't miss the chance to thank Barbara Valeriani-Kaminski and, my BCGS friends in particular Abhay, Aniket, Abhilash, Rohan, Deepankan, Niraj, Akhilesh, and Kamal. I am grateful for all your support and the fun times we had.

Last, but not the least, I would like  to thank my family for their support and love. Without their help and many words of encouragement, it would have been more difficult for me to pursue and finish my studies.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../mythesis"
%%% End: 
